On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence

### 2017-09-18 Thesis/Draft.tex
final

{\large Master's Thesis submitted\\\vspace{0.5cm}
    to}
    \\\vspace{0.5cm}
    {\large{\bf Prof. Dr. Marius Kloft \\}}
    {\large{\bf Prof. Alexandra Carpentier, PhD \\}}
    \vspace{0.5cm}

@@

    {\large in partial fulfillment of the requirements \\
    for the degree of \\
    {\bf Master of Science (M. Sc.)\\} \vspace{3cm}
    Berlin, September 18, 2017\\}

@@

Consider the problem the latter companies face. Whenever a user reports
that she visited a restaurant, the app would like to ask questions about
her experience. To give a simple example, assume users are not willing
to answer more than one question per restaurant visit, and the app would
like to find out two things: Does the restaurant have good service? Is
the restaurant trendy? See \autoref{app:Foursquare} for how this
information is then displayed in the Foursquare app.

@@

\section{Example of User Feedback in Foursquare App} \label{app:Foursquare}

\begin{figure}[htbp]
\centering
\includegraphics{figures/Foursquare_Screenshot.png}
\caption{The right screenshot shows aggregated user feedback in the
Foursquare app. One could use thresholding bandit algorithms as
presented in this thesis to ask different questions so as to optimize
the confidence with which the results are displayed for a restaurant in
the app.}
\end{figure}

@@

In order to assess the excellent performance of the Bayes-UCB algorithm,
which comes at a surprise given that is is designed for the cumulative
regret setting and thus should tend to explore the arms less, we run the
Bayes-UCB algorithm for simulation 2 with three different choices of the
parameter \(c\). In Figure 15, we see the performance results of the
three versions, whereas Figure 16 shows how the algorithm allocates its
budget across the arms over time. The three versions differ in the
quantile parameter \(c\) (compare \autoref{app:AppendixBUCB}) for which
we choose \(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann
et al. (2012a), the cumulative regret upper bound for the Bayes-UCB is
shown for \(c\geq 5\), though they report that the choice of \(c=0\)
worked much better in their experiments. In our problem, it also makes
sense that the versions with smaller quantiles (smaller \(c\)) tend to
perform better, as these correspond to more exploration of the arms. In
this particular simulation, the choices of \(c=1/5\) and \(c=1\) perform
very similar. We see that the worse performance of \(c=5\) can be
attributed to a long initial phase of sampling primarily the arms with
mean below the threshold. This comes from the fact that the Bernoulli
and Beta distributions are bounded between \(0\) and \(1\), with
\(\tau\) very close to \(0\). Thus, the index \(B_i^{BUCB}(t)\) cannot
be larger than \(\tau\) for arms with \(\hat{\mu}_i(t) \geq \tau\). For
arms with \(\hat{\mu}_i(t) < \tau\), however, the index can be as large
as \(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 14:
Due to \(c=5\), the indexes are based on very large quantiles even in
the beginning, which leads to large indexes for the arms with small
means. This however is not the ideal sampling behavior. The other two
variants adapt much better due to their smaller quantiles (and more
exploration).

@@

In Figure 17, we show the distribution of \(T_6(T)\) for algorithms APT,
Bayes-UCB, and SLR. We see that the distribution of the Bayes-UCB
algorithm is much better concentrated around the optimal share of the
budget, and has a bell curve shape. In contrast, the distributions of
APT and SLR are much less concentrated but flat and wide, and spread
across a very large interval. Both algorithms have several iterations in
which they draw arm 6--the most difficult arm--only a single time
(during initialization). This happens for APT in more than 5\% of the
iterations, and leads to the spike on the very left of the graph. In
order to cope at least a little bit with this problem, we have also run
the SLR algorithm with the D-Tracking rule as introduced in Garivier and
Kaufmann (2016). The effect is barely noticeable in Figure 17, but the
minimum number of observations is now clearly bounded away from 0. The
effect on the performance was described before and is very noticeable in
comparison to SLR without D-Tracking. However, even with D-Tracking the
performance of Bayes-UCB is not reached. We describe SLR with D-Tracking
in Algorithm 5.

>>>>

{\large Master's Thesis submitted\\\vspace{0.5cm}
    to}
    \\\vspace{0.5cm}
    {\large{\bf Prof. Dr. Marius Kloft \\}}
    {\large{\bf Dr. Alexandra Carpentier \\}}
    \vspace{0.5cm}

@@

    {\large in partial fulfillment of the requirements \\
    for the degree of \\
    {\bf Master of Science (M. Sc.) in Statistics\\} \vspace{3cm}
    Berlin, September 18, 2017\\}

@@

Consider the problem the latter companies face. Whenever a user reports
that she visited a restaurant, the app would like to ask questions about
her experience. To give a simple example, assume users are not willing
to answer more than one question per restaurant visit, and the app would
like to find out two things: Does the restaurant have good service? Is
the restaurant trendy?

@@

@@

In order to assess the excellent performance of the Bayes-UCB algorithm,
which comes at a surprise given that is is designed for the cumulative
regret setting and thus should tend to explore the arms less, we run the
Bayes-UCB algorithm for simulation 2 with three different choices of the
parameter \(c\). In Figure 14, we see the performance results of the
three versions, whereas Figure 15 shows how the algorithm allocates its
budget across the arms over time. The three versions differ in the
quantile parameter \(c\) (compare \autoref{app:AppendixBUCB}) for which
we choose \(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann
et al. (2012a), the cumulative regret upper bound for the Bayes-UCB is
shown for \(c\geq 5\), though they report that the choice of \(c=0\)
worked much better in their experiments. In our problem, it also makes
sense that the versions with smaller quantiles (smaller \(c\)) tend to
perform better, as these correspond to more exploration of the arms. In
this particular simulation, the choices of \(c=1/5\) and \(c=1\) perform
very similar. We see that the worse performance of \(c=5\) can be
attributed to a long initial phase of sampling primarily the arms with
mean below the threshold. This comes from the fact that the Bernoulli
and Beta distributions are bounded between \(0\) and \(1\), with
\(\tau\) very close to \(0\). Thus, the index \(B_i^{BUCB}(t)\) cannot
be larger than \(\tau\) for arms with \(\hat{\mu}_i(t) \geq \tau\). For
arms with \(\hat{\mu}_i(t) < \tau\), however, the index can be as large
as \(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 13:
Due to \(c=5\), the indexes are based on very large quantiles even in
the beginning, which leads to large indexes for the arms with small
means. This however is not the ideal sampling behavior. The other two
variants adapt much better due to their smaller quantiles (and more
exploration).

@@

In Figure 16, we show the distribution of \(T_6(T)\) for algorithms APT,
Bayes-UCB, and SLR. We see that the distribution of the Bayes-UCB
algorithm is much better concentrated around the optimal share of the
budget, and has a bell curve shape. In contrast, the distributions of
APT and SLR are much less concentrated but flat and wide, and spread
across a very large interval. Both algorithms have several iterations in
which they draw arm 6--the most difficult arm--only a single time
(during initialization). This happens for APT in more than 5\% of the
iterations, and leads to the spike on the very left of the graph. In
order to cope at least a little bit with this problem, we have also run
the SLR algorithm with the D-Tracking rule as introduced in Garivier and
Kaufmann (2016). The effect is barely noticeable in Figure 16, but the
minimum number of observations is now clearly bounded away from 0. The
effect on the performance was described before and is very noticeable in
comparison to SLR without D-Tracking. However, even with D-Tracking the
performance of Bayes-UCB is not reached. We describe SLR with D-Tracking
in Algorithm 5.
